---
title: "gpof item correlations"
author: "Will Hall"
date: "07/02/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, echo = FALSE, message=FALSE, warning=FALSE, results = "hide"}
library(tidyverse)
library(here)

data_raw <- 
	haven::read_sav(here("working/GPOF_February 4 2021_FINAL.sav"))

data_reduced <- 
	data_raw %>% 
	select(PID, Sex_Condition, 
				 starts_with("Agen_", ignore.case = FALSE), 
				 starts_with("Comm_", ignore.case = FALSE)) %>% 
	rename_with(tolower) %>% 
	mutate(target_gender = case_when(sex_condition == 0 ~ "male", 
																	 sex_condition == 1 ~ "female")) %>% 
	relocate(target_gender, .before = sex_condition) %>% 
	drop_na(target_gender) %>% 
	select(-sex_condition)

good_pids <- 
	data_raw %>% 
	select(PID, good_data = `filter_$`) %>% 
	filter(good_data == 1) %>% 
	pull(PID) %>% 
	as.character()

fm_corr <- 
data_reduced %>% 
	filter(pid %in% good_pids) %>% 
	pivot_longer(-c(pid, target_gender)) %>% 
	mutate(item = case_when(str_detect(name, "1") ~ "one", 
													str_detect(name, "2") ~ "two")) %>% 
	mutate(name = str_remove_all(name, "1|2")) %>% 
	arrange(name) %>% 
	pivot_wider(names_from = item, values_from = value) %>% 
	nest(data = c(pid, one, two)) %>% 
	mutate(cor_test = data %>% map(~cor.test(.$one, .$two, data = .)), 
				 cor_test_tidy = cor_test %>% map(broom::tidy, conf.int = TRUE))



p1 <- 
fm_corr %>% 
	unnest(cor_test_tidy) %>% 
	ungroup %>% 
	mutate(name = tidytext::reorder_within(name, estimate, as.factor(target_gender))) %>% 
	ggplot(aes(x = name, y = estimate)) + 
	geom_pointrange(aes(ymax = conf.high, ymin = conf.low)) + 
	facet_wrap(~target_gender, scales = "free_y" ) +
	coord_flip() + 
	tidytext::scale_x_reordered() +
	labs(y = "r", title = "The relationship between ratings on the first and second vignette.",
			 subtitle = "The error bars are 95% CIs")

# overall -----------------------------------------------------------------

cor_overall_fm <- 
data_reduced %>% 
	filter(pid %in% good_pids) %>% 
	pivot_longer(-c(pid, target_gender)) %>% 
	mutate(item = case_when(str_detect(name, "1") ~ "one", 
													str_detect(name, "2") ~ "two")) %>% 
	mutate(name = str_remove_all(name, "1|2")) %>% 
	pivot_wider(names_from = item, values_from = value) %>% 
	separate(name, into = c("type", "domain","trait")) %>% 
	unite("error_type", type, domain) %>% 
	group_by(pid, error_type, target_gender) %>% 
	summarise(one_mean = mean(one, na.rm = TRUE), 
						two_mean = mean(two, na.rm = TRUE)) %>% 
	nest(data = -c(error_type, target_gender)) %>% 
	mutate(cor_test = data %>% map(~cor.test(.$one_mean, .$two_mean, data = .)), 
				 cor_test_tidy = cor_test %>% map(broom::tidy, conf.int = TRUE))

p2 <- 
cor_overall_fm %>% 
	unnest(cor_test_tidy) %>% 
  ungroup %>% 
	mutate(error_type = tidytext::reorder_within(error_type, estimate, as.factor(target_gender))) %>% 
	ggplot(aes(x = error_type, y = estimate)) + 
	geom_pointrange(aes(ymax = conf.high, ymin = conf.low)) + 
	facet_wrap(~target_gender, scales = "free_y" ) +
	coord_flip() + 
	tidytext::scale_x_reordered() + 
	labs(y = "r", title = "The relationship between the overall ratings on the first and second vignette.",
			 subtitle = "The error bars are 95% CIs")



```
## Overview

These plots show the correlations between the first and second vignette for the different vignette types. For both plots, the x-axis is the correlations coefficient (*r*). The y-axis is ordered by the strength of the relationship. 

## Item level correlations

This plot shows the correlations at the item level. E.g., what is the correlation between `Agen_Work_Skillful_1` and `Agen_Work_Skillful_2`. 

```{r fig.height = 13, fig.width = 13}
p1 + theme(text = element_text(size=15))
```

## Overall relationships

This plot shows the correlations between the two composite ratings for each error type. E.g., what's the correlation between the two vignettes about forgetting something agentic at work.

```{r}
p2
```

